---
title: "Real Estate Prediction - Kaggle"
output: html_notebook
---
```{r}
library(dplyr)
library(tidyr)
library(corrplot)
```

This is a notebook compiling the steps and methods used to predict home sale price for the kaggle competition [https://www.kaggle.com/c/house-prices-advanced-regression-techniques].

```{r load_data}
file_path = file.path("C:", "Users", "l2eve", "Documents", "Kaggle", "train_real-estate.csv")
df = read.csv(file_path)
```
This is a view of the basic structure of the whole data set.  In this competition we are to predict the sale price of the real estate.
```{r examine_data}
head(df)
str(df)
summary(df)
```

Below is a histogram of the Sales Price Data to help understand the overall shape of the data.  There are a few outliers that will need to be explained in order to get a solid model, however the full data appears to be pretty close to normal, though it will never have a non-zero so a different distrubution may yield better results.

```{r sales_histogram}
p = ggplot(df, aes(SalePrice)) +
        geom_histogram() +
        ggtitle("Histogram of Sale Price")
print(p)
```


Below is data that is only numeric in nature, though some of them will likely need to be reclassified as factors.
```{r select_numeric-only}
nums = sapply(df, is.numeric)
head(df[,nums])
dim(df[,nums])
```
```{r, width = 8, height = 8}
corrplot(cor(df[,nums]))
```

As a baseline, I will create a regression model based on "intuitive" use of the variables proveded.  Hopefully, after more rigorous analysis each subsequent model will outperform this baseline.

```{r}
baseline_lm = lm(SalePrice ~ Neighborhood + Condition1 + BldgType + HouseStyle + YearBuilt + TotalBsmtSF + X1stFlrSF + X2ndFlrSF + GarageCars + MoSold + YrSold + SaleType, df)
test_path = file.path("C:", "Users", "l2eve", "Documents", "Kaggle", "test_real_estate.csv")
test_df = read.csv(test_path)
pred_baseline = predict(baseline_lm, test_df)
summary(baseline_lm)
summary(pred_baseline)
plot(pred_baseline)
class(pred_baseline)
names(pred_baseline) = seq(from = 1461, to = length(pred_baseline)+1460)
head(pred_baseline)
length(pred_baseline)
pred_baseline[is.na(pred_baseline)] = median(pred_baseline, na.rm = TRUE)
write_test = file.path("C:", "Users", "l2eve", "Documents", "Kaggle", "baseline_test.csv")
write.csv(pred_baseline, write_test)
```


